Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-21 paper_jasa.tex
p-value plot changed to square root scale
New section added

\hh{From figure \ref{fig:power_loess_effect} we see that identification of the data plot is high independently of the effect size for experiment 3. This might be an indication that participants were not considering slope as distinguishing feature for the data, but the apparent clustering, i.e. the null hypothesis is being rejected, but not for the reason of the slope -- which the experimental setup was asking for --  leading to a type III error of correctly rejecting the null hypothesis for the wrong reason', as defined by \citet{mosteller:48}.} \green{Not sure that this goes here, but something needs to be said about Type III.} \blue{We also see this feature in figure \ref{fig:choice_reason}}.

@@

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.6}{\includegraphics{p_val_plot_signal.pdf}}
       \caption{Conventional test $p$-value ($p_D$) vs plot signal strength ($\hat p_D$) estimated using Lemma \ref{lemma}. The solid line is a 45 degree line which represents the equity shown in equation \ref{eqn:power_estimate}. p-values are shown on log scale.}
    %   \hh{Mahbub, another change: could you change the y label to 'estimate of visual p-value $\hat{p_D}$ ?}
       \label{fig:pval_plot_signal}
\end{figure*}

@@

>>>>

@@

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.6}{\includegraphics{p_val_plot_signal.pdf}}
       \caption{Conventional test $p$-value ($p_D$) vs plot signal strength ($\hat p_D$) estimated using Lemma \ref{lemma}. The solid line is a 45 degree line which represents the equity shown in equation \ref{eqn:power_estimate}. p-values are shown on square root scale scale. \blue{Is it better now?}}
    %   \hh{Mahbub, another change: could you change the y label to 'estimate of visual p-value $\hat{p_D}$ ?}
       \label{fig:pval_plot_signal}
\end{figure*}

@@

\subsection{Alternative - Type III error}

\hh{From figure \ref{fig:power_loess_effect} we see that identification of the data plot is high independently of the effect size for experiment 3. This might be an indication that participants were not considering slope as distinguishing feature for the data, but the apparent clustering, i.e. the null hypothesis is being rejected, but not for the reason of the slope -- which the experimental setup was asking for --  leading to a type III error of correctly rejecting the null hypothesis for the wrong reason', as defined by \citet{mosteller:48}.}

%\green{Not sure that this goes here, but something needs to be said about Type III.}

\blue{We also see this feature in figure \ref{fig:choice_reason}}.
